**Preprinting Microbiology**

### 2017-03-13 submission/Schloss_PrePrints_mBio_2017.Rmd
Add sentence about possible COI of Bik paper
Closes #7

Second, preprints have proven useful for rapidly correcting the scientific literature. On February 9, 2015, *Cell Systems* posted a study by Afshinnekoo et al. online [@Afshinnekoo2015a]. The study collected and analyzed metagenomic sequence data from the New York City subway system and reported finding *Yersinia pestis* and *Bacillus anthracis*. Because of the focus on these two bioterrorism agents, this study generated a considerable amount of media attention. On April 25, 2015, Petit et al. [@Petit2015] posted a preprint to Zenodo demonstrating that there was no evidence for *B. anthracis* in the dataset. On July 29, 2015, a critique was published by *Cell Systems* along with a response from the original authors offering a correction to their manuscript [@Ackelsberg2015; @Afshinnekoo2015b]. A second anecdote of using preprints to aid in post-publication peer-review surrounds the publishing of a draft tardigrade genome in *The Proceedings of the National Academy of Sciences*. On November 23, 2015 a study by Boothby et al. [@Boothby2015] was first published online. The authors claimed that 17.5% of its genes came from bacteria, archaea, fungi, plants, and viruses. Another group had been analyzing sequence data from a parallel tardigrade genome sequencing project and did not observe the same result. A week later, on December 1, 2015, the second group had posted a preprint comparing the two genome sequences and demonstrating that the exciting claims of horizontal gene transfer were really the product of contaminants [@Koutsovoulos2016a]; this analysis would eventually be published online by the original journal on March 24, 2016 followed by a rebuttal by the original authors on May 31, 2016 [@Boothby2016; @Koutsovoulos2016b]. Two other analyses of the original data were published in May 2016 and a third was posted as a preprint on February 2, 2016 [@Bemm2016; @Arakawa2016; @Delmont2016]. These anecdotes underscore the value of having a rapid posting cycle to correcting errors in the scientific literature and that results posted to preprint servers were able to correct the record within weeks of the initial publication while the traditional path took six months in both cases. A final notable case where preprints have accelerated the correction of the scientific record was a preprint posted by Bik et al. reporting numerous cases of image manipulation in peer reviewed studies [@Bik2016a]. Their preprint was posted on April 20, 2016 and published in *mBio* on June 7, 2016 [@Bik2016b]. Instead of using preprints to react to published papers that have been through peer review, it would be interesting to consider how the editorial process for these examples and the infamous "Arsenic Life" paper [@WolfeSimon2010] would have been different had they initially been posted as preprints.

>>>>

Second, preprints have proven useful for rapidly correcting the scientific literature. On February 9, 2015, *Cell Systems* posted a study by Afshinnekoo et al. online [@Afshinnekoo2015a]. The study collected and analyzed metagenomic sequence data from the New York City subway system and reported finding *Yersinia pestis* and *Bacillus anthracis*. Because of the focus on these two bioterrorism agents, this study generated a considerable amount of media attention. On April 25, 2015, Petit et al. [@Petit2015] posted a preprint to Zenodo demonstrating that there was no evidence for *B. anthracis* in the dataset. On July 29, 2015, a critique was published by *Cell Systems* along with a response from the original authors offering a correction to their manuscript [@Ackelsberg2015; @Afshinnekoo2015b]. A second anecdote of using preprints to aid in post-publication peer-review surrounds the publishing of a draft tardigrade genome in *The Proceedings of the National Academy of Sciences*. On November 23, 2015 a study by Boothby et al. [@Boothby2015] was first published online. The authors claimed that 17.5% of its genes came from bacteria, archaea, fungi, plants, and viruses. Another group had been analyzing sequence data from a parallel tardigrade genome sequencing project and did not observe the same result. A week later, on December 1, 2015, the second group had posted a preprint comparing the two genome sequences and demonstrating that the exciting claims of horizontal gene transfer were really the product of contaminants [@Koutsovoulos2016a]; this analysis would eventually be published online by the original journal on March 24, 2016 followed by a rebuttal by the original authors on May 31, 2016 [@Boothby2016; @Koutsovoulos2016b]. Two other analyses of the original data were published in May 2016 and a third was posted as a preprint on February 2, 2016 [@Bemm2016; @Arakawa2016; @Delmont2016]. These anecdotes underscore the value of having a rapid posting cycle to correcting errors in the scientific literature and that results posted to preprint servers were able to correct the record within weeks of the initial publication while the traditional path took six months in both cases. A final notable case where preprints have accelerated the correction of the scientific record was a preprint posted by Bik et al. [@Bik2016a] reporting numerous cases of image manipulation in peer reviewed studies. This was a case where a journal may have been reluctant to publish the findings because it could have put the journal in a bad light. Posting the manuscript as a preprint removed potential conflicts of interests from journals that could have hindered its ability to be published. After the preprint was posted on April 20, 2016 it was published in *mBio* on June 7, 2016 [@Bik2016b]. Instead of using preprints to react to published papers that have been through peer review, it would be interesting to consider how the editorial process for these examples and the infamous "Arsenic Life" paper [@WolfeSimon2010] would have been different had they initially been posted as preprints.
